Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/model.tex
fix typo

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector of containing $N$
  integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
  An equivalent view of these vectors is as an $N$-times Cartesian
  product on subsets of $\bz$.
  We use $S, T, U$ to denote index schemes. Henceforth, we assume index schemes
  are all $N$-dimensional\footnote{The particular
    dimensionality is derived from array types when the model is
    used.} for some $N$.

>>>>

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector containing $N$
  integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
  An equivalent view of these vectors is as an $N$-times Cartesian
  product on subsets of $\bz$.
  We use $S, T, U$ to denote index schemes. Henceforth, we assume index schemes
  are all $N$-dimensional\footnote{The particular
    dimensionality is derived from array types when the model is
    used.} for some $N$.
